Environmental warming increases the importance of high-turnover energy channels in stream food webs

### 2022-12-23 doc/ms/Junker_temp-energy-flux_submission.Rmd
getting ready to transfer over to new repo and submit

---
title: "Environmental warming increases the importance of high-turnover energy channels in stream food webs"
author:
  - James R. Junker:
      email: jrjunker@mtu.edu
      institute: [msu, glrc]
      correspondence: true
  - name: Wyatt F. Cross
    institute: msu
  - name: James M. Hood
    institute: osu
  - name: Jonathan P. Benstead
    institute: bama
  - name: Alexander D. Huryn
    institute: bama
  - name: Daniel Nelson
    institute: usu
  - name: Jón S. Ólafsson
    institute: veidi
  - name: Gísli M. Gíslason
    institute: reyk
institute:
  - msu: Department of Ecology, Montana State University, Bozeman, MT 59717, USA
  - glrc: Current `address:` Great Lakes Research Center, Michigan Technological University, Houghton, MI 49931, USA
  - osu: Department of Evolution, Ecology, and Organismal Biology, The Ohio State University, Translational Data Analytics Institute, The Aquatic Ecology Laboratory, Columbus, OH 43212, USA
  - bama: Department of Biological Sciences, University of Alabama, Tuscaloosa, AL  35487, USA
  - usu: National Aquatic Monitoring Center, Department of Watershed Sciences, Utah State University, Logan, UT 84322, USA
  - veidi: Institute of Marine and Freshwater Fisheries, Hafnarfjördur, Iceland
  - reyk: University of Iceland, Institute of Life and Environmental Sciences, Reykjavík, Iceland
output:
   word_document:
      reference_docx: working_docx_template.docx
      toc: no
      pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
      - '--filter=pandoc-crossref.exe'
   pdf_document:
     keep_tex: true
   html_document: default
   pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
      - '--filter=pandoc-crossref.exe'
header-includes:
- \usepackage{lineno}
- \usepackage{amsmath}
- \numberwithin{equation}
- \usepackage{indentfirst}
- \linenumbers
indent: true
linestretch: 1
bibliography: refs.bib
link-citations: no
link-color: grey
csl: ecology.csl
---

@@

```{r trait v temp, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=5, dpi = 450, fig.cap="Figure 1. (A) Total organic matter flux (g AFDM m^-2^ y^-1^) increased with mean annual temperature. Higher stream temperatures also led to (B) a decrease in mean population body size ($\\overline{M}$, mg ind^-1^) and (C) an increase in mean population biomass turnover rate ($\\overline{P:B}$, y^-1^). For all panels, points represent the mean value, wide bars represent the 25^th^ and 75^th^ percentile bounds, and narrow bars represent the 2.5^th^ and 97.5^th^ percentile bounds."}

@@

```{r M lorenz analysis, echo =FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=4, dpi = 450, fig.cap="Figure 3. (A) Lorenz curves showing cumulative relative organic matter flux among taxa with increasing body size (from left to right; *M*, mg AFDM ind^-1^). The solid line 1:1 line from the origin represents the line of equality. Distributions near this line suggest minimal structuring of OM fluxes in relation to body size. The dotted line allows for visualization of skewness in OM fluxes based on its intersection with the empirical lorenz curve. (B) Empirical estimates of body size-related OM flux skewness in relation to stream temperature. (C) The probability of observing these skewness values when compared to a random ordering. For panels B and C, points represent the median value, wide bars represent the 25^th^ and 75^th^ percentile bounds, and narrow bars represent the 2.5^th^ and 97.5^th^ percentile bounds."}

@@

```{r skew prob temp, echo = FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=4, dpi = 450, fig.cap="Figure 4. (A) Lorenz curves showing cumulative relative organic matter flux among taxa with increasing *P:B* ratio (from left to right; y^-1^). The solid 1:1 line from the origin represents the line of equality. Distributions near this line suggest minimal structuring of OM fluxes in relation to *P:B* ratio. The dotted line allows for visualization of skewness in OM fluxes based on its intersection with the Lorenz curve. (B) Estimates of *P:B*-related OM flux skewness in relation to stream temperature. (C) The probability of observing these skewness values when compared to a random (i.e., stochastic) ordering. For panels B and C, points represent the median value, wide bars represent the 25^th^ and 75^th^ percentile bounds, and narrow bars represent the 2.5^th^ and 97.5^th^ percentile bounds." }

drake::loadd(PB_lorenz_skew_fig)
grid.draw(PB_lorenz_skew_fig)
```

@@

>>>>

---
title: "Environmental warming increases the importance of high-turnover energy channels in stream food webs"
author:
  - James R. Junker:
      email: jrjunker@mtu.edu
      institute: [msu, glrc]
      correspondence: true
  - name: Wyatt F. Cross
    institute: msu
  - name: James M. Hood
    institute: osu
  - name: Jonathan P. Benstead
    institute: bama
  - name: Alexander D. Huryn
    institute: bama
  - name: Daniel Nelson
    institute: usu
  - name: Jón S. Ólafsson
    institute: veidi
  - name: Gísli M. Gíslason
    institute: reyk
institute:
  - msu: Department of Ecology, Montana State University, Bozeman, MT 59717, USA
  - glrc: Current `address:` Great Lakes Research Center, Michigan Technological University, Houghton, MI 49931, USA
  - osu: Department of Evolution, Ecology, and Organismal Biology, The Ohio State University, Translational Data Analytics Institute, The Aquatic Ecology Laboratory, Columbus, OH 43212, USA
  - bama: Department of Biological Sciences, University of Alabama, Tuscaloosa, AL  35487, USA
  - usu: National Aquatic Monitoring Center, Department of Watershed Sciences, Utah State University, Logan, UT 84322, USA
  - veidi: Institute of Marine and Freshwater Fisheries, Hafnarfjördur, Iceland
  - reyk: University of Iceland, Institute of Life and Environmental Sciences, Reykjavík, Iceland
output:
   word_document:
      reference_docx: docx_template.docx
      toc: no
      pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
      - '--filter=pandoc-crossref.exe'
   pdf_document:
     keep_tex: true
   html_document: default
   pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
      - '--filter=pandoc-crossref.exe'
header-includes:
- \usepackage{lineno}
- \usepackage{amsmath}
- \numberwithin{equation}
- \usepackage{indentfirst}
- \linenumbers
indent: true
linestretch: 1
bibliography: refs.bib
link-citations: no
link-color: grey
csl: ecology.csl
---

@@

@@

@@

@@

# Figure captions

Figure 1. (A) Total organic matter flux (g AFDM m^-2^ y^-1^) increased with mean annual temperature. Higher stream temperatures also led to (B) a decrease in mean population body size ($\\overline{M}$, mg ind^-1^) and (C) an increase in mean population biomass turnover rate ($\\overline{P:B}$, y^-1^). For all panels, points represent the mean value, wide bars represent the 25^th^ and 75^th^ percentile bounds, and narrow bars represent the 2.5^th^ and 97.5^th^ percentile bounds.

Figure 2. (A) Log~10~ percent contribution of taxa to OM flux in each stream; colors correspond to mean annual temperature shown in the legend; (B) rank-ordered organic matter flux (log~e~(mg AFDM m^-2^ y^-1^) by taxon. Taxa abbreviations: F:Naid, Family Naididae; N comm, *Nais communis*; C syl, *Cricotopus sylvestris*; R balt, *Radix balthica*; Macro sp., *Macropelopia* sp.; C dent, *Chaetocladius dentiforceps*; S vitt, *Simulium vittatum*; Euk spp., *Eukiefferiella* spp.; O obl, *Orthocladius oblidens*; Micro sp. *Micropsectra* sp.; D bert, *Diamesa bertrami*; D boh-zer, *Diamesa bohemani-zernyi*; F: Lumb, Family Lumbricidae; P cing, *Potamophylax cingulatus*; S gland, *Sperchon glandulosus*; P urs, *Prosimulium ursinum*; SC: Cope, Subclass Copepoda; R eff, *Rheocricotopus effusus*; S vern, *Simulium vernum*; Chaet sp., *Chaetocladius* sp.; Thien sp., *Thienemanniella*  sp.; O frig, *Orthocladius frigidus*; Limn rip, *Limnophora riparia*; Dicra, *Dicranota* sp.; C: Ost, Class Ostracoda; S aur, *Simulium aurem*.

Figure 3. (A) Lorenz curves showing cumulative relative organic matter flux among taxa with increasing body size (from left to right; *M*, mg AFDM ind^-1^). The solid line 1:1 line from the origin represents the line of equality. Distributions near this line suggest minimal structuring of OM fluxes in relation to body size. The dotted line allows for visualization of skewness in OM fluxes based on its intersection with the empirical lorenz curve. (B) Empirical estimates of body size-related OM flux skewness in relation to stream temperature. (C) The probability of observing these skewness values when compared to a random ordering. For panels B and C, points represent the median value, wide bars represent the 25^{th} and 75^{th} percentile bounds, and narrow bars represent the 2.5^{th} and 97.5^{th} percentile bounds.

Figure 4. (A) Lorenz curves showing cumulative relative organic matter flux among taxa with increasing *P:B* ratio (from left to right; y^{-1}). The solid 1:1 line from the origin represents the line of equality. Distributions near this line suggest minimal structuring of OM fluxes in relation to *P:B* ratio. The dotted line allows for visualization of skewness in OM fluxes based on its intersection with the Lorenz curve. (B) Estimates of *P:B*-related OM flux skewness in relation to stream temperature. (C) The probability of observing these skewness values when compared to a random (i.e., stochastic) ordering. For panels B and C, points represent the median value, wide bars represent the 25^{th} and 75^{th} percentile bounds, and narrow bars represent the 2.5^{th} and 97.5^{th} percentile bounds.

## Figure 1

```{r figure 1, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=5, dpi = 450, fig.cap="Figure 1. (A) Total organic matter flux (g AFDM m^-2^ y^-1^) increased with mean annual temperature. Higher stream temperatures also led to (B) a decrease in mean population body size ($\\overline{M}$, mg ind^-1^) and (C) an increase in mean population biomass turnover rate ($\\overline{P:B}$, y^-1^). For all panels, points represent the mean value, wide bars represent the 25^th^ and 75^th^ percentile bounds, and narrow bars represent the 2.5^th^ and 97.5^th^ percentile bounds."}

## Figure 2

## Figure 3

```{r figure 3, echo =FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=4, dpi = 450, fig.cap="Figure 3. (A) Lorenz curves showing cumulative relative organic matter flux among taxa with increasing body size (from left to right; *M*, mg AFDM ind^-1^). The solid line 1:1 line from the origin represents the line of equality. Distributions near this line suggest minimal structuring of OM fluxes in relation to body size. The dotted line allows for visualization of skewness in OM fluxes based on its intersection with the empirical lorenz curve. (B) Empirical estimates of body size-related OM flux skewness in relation to stream temperature. (C) The probability of observing these skewness values when compared to a random ordering. For panels B and C, points represent the median value, wide bars represent the 25^th^ and 75^th^ percentile bounds, and narrow bars represent the 2.5^th^ and 97.5^th^ percentile bounds."}

## Figure 4

```{r figure 4, echo = FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=4, dpi = 450, fig.cap="Figure 4. (A) Lorenz curves showing cumulative relative organic matter flux among taxa with increasing *P:B* ratio (from left to right; y^-1^). The solid 1:1 line from the origin represents the line of equality. Distributions near this line suggest minimal structuring of OM fluxes in relation to *P:B* ratio. The dotted line allows for visualization of skewness in OM fluxes based on its intersection with the Lorenz curve. (B) Estimates of *P:B*-related OM flux skewness in relation to stream temperature. (C) The probability of observing these skewness values when compared to a random (i.e., stochastic) ordering. For panels B and C, points represent the median value, wide bars represent the 25^th^ and 75^th^ percentile bounds, and narrow bars represent the 2.5^th^ and 97.5^th^ percentile bounds." }

drake::loadd(PB_lorenz_skew_fig)
grid.draw(PB_lorenz_skew_fig)
